The thin blue line:\\what protects my Android device?

### 2015-03-25 securityupdates.tex
Move paragraph about showing standard deviations

@@

Where possible we indicate the uncertainty in our results by presenting them $\pm$ one standard deviation and give results to 3 significant figures, this occasionally results in `${} \pm 0$' when the standard deviation is less than the number of significant figures.
This technique cannot account for systematic errors which we explore in \S\ref{sec:representative}.

>>>>

Where possible we indicate the uncertainty in our results by presenting them $\pm$ one standard deviation and give results to 3 significant figures, this occasionally results in `$\pm\, 0$' when the standard deviation is small.
This technique cannot account for systematic errors which we explore in \S\ref{sec:representative}.

@@
